Mood increases during video game play: A naturalistic observational case study of PowerWash Simulator

### 2023-09-06 ms.qmd
Fix build

date: 2023-09-04
bibliography: bibliography.bib
format:
  docx: default
  html: default
---

@@

$$
\begin{align*}
\text{mood}_{ijk} &\sim \text{CensNormal}(\eta_{ijk}, \sigma^2, 0, 1), \\
\eta_{ijk} &= \alpha_0 + \beta_{0j} +
  (\alpha_1 + \beta_{1j})\text{post}_{ijk} +
  \gamma_{0k}, \\
\begin{bmatrix} \alpha_0 \\ \alpha_1 \end{bmatrix} &\sim 
  \text{MVN}\left(\begin{bmatrix} 0 \\ 0 \end{bmatrix}, 
  \begin{bmatrix} 
    \tau_{\alpha_0} &\rho_{{\alpha_0}{\alpha_1}} \\ 
    \rho_{{\alpha_0}{\alpha_1}} &\tau_{\alpha_1}
  \end{bmatrix}\right), \\
  \gamma_0 &\sim \text{Normal}(0, \tau_{\gamma_0}).
\end{align*}
$$

```{r}
#| label: model-estimate

@@

model <- bf(mood ~ 1 + post + (1 + post | pid) + (1 | ps)) +
  gaussian()

fit <- brm(
  model,
  data = dat,
  silent = 0, # Required for printing mcmc progress on some systems
  threads = 2,
  iter = 500,
  control = list(adapt_delta = .95),
  file = "models/brm-pre-post-pid-ps"
)
```

```{r}
#| label: model-build

model <- bf(mood ~ 1 + post + (1 + post |p| pid) + (1 | ps)) +
  lf(sigma ~ 1 + (1 |p| pid)) +
  gaussian()

fit2 <- brm(
  model,
  data = dat,
  silent = 0,
  threads = 2,
  iter = 500,
  control = list(adapt_delta = .95),
  file = "models/brm-pre-post-pid-ps-scale"
)

model <- bf(mood ~ 1 + post + (1 + post |p| pid)) +
  lf(sigma ~ 1 + (1 |p| pid)) +
  gaussian()

fit3 <- brm(
  model,
  data = dat,
  silent = 0,
  threads = 2,
  iter = 500,
  control = list(adapt_delta = .95),
  file = "models/brm-pre-post-pid-scale"
)

@@

fit4 <- brm(
  model,
  data = dat,
  silent = 0,
  threads = 2,
  iter = 500,
  control = list(adapt_delta = .95),
  file = "models/brm-pre-post-pid-ps-censored"
)
fit <- fit4
```

@@

library(posterior)
as_draws(fit4, variable = c("b_", "sd_", "cor_"), regex = TRUE) |> 
  summarise_draws(rhat)
pairs(fit4$fit, pars = variables(fit)[1:7])
```

>>>>

date: 2023-09-04
bibliography: bibliography.bib
format:
  pdf: default
  docx: default
  html: default
---

@@

\begin{align*}
\text{mood}_{ijk} &\sim \text{CensNormal}(\eta_{ijk}, \sigma^2, 0, 1), \\
\eta_{ijk} &= \alpha_0 + \beta_{0j} +
  (\alpha_1 + \beta_{1j})\text{post}_{ijk} +
  \gamma_{0k}, \\
\begin{bmatrix} \alpha_0 \\ \alpha_1 \end{bmatrix} &\sim 
  \text{MVN}\left(\begin{bmatrix} 0 \\ 0 \end{bmatrix}, 
  \begin{bmatrix} 
    \tau_{\alpha_0} &\rho_{{\alpha_0}{\alpha_1}} \\ 
    \rho_{{\alpha_0}{\alpha_1}} &\tau_{\alpha_1}
  \end{bmatrix}\right), \\
  \gamma_0 &\sim \text{Normal}(0, \tau_{\gamma_0}).
\end{align*}

```{r}
#| label: model-estimate
#| cache: false

@@

@@

fit <- brm(
  model,
  data = dat,
  silent = 0,
  threads = 2,
  iter = 2000,
  control = list(adapt_delta = .95),
  file = "models/brm-pre-post-pid-ps-censored"
)
```

@@

library(posterior)
as_draws(fit, variable = c("b_", "sd_", "cor_"), regex = TRUE) |> 
  summarise_draws(rhat)
pairs(fit$fit, pars = variables(fit)[1:7])
```
